---
title: "Plotting the Solar System"
author: "Arthur Luna - arthurluna@outlook.com"
date: "18/06/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, cache = T, warning = F)
```

## What is this app?

This app was done to explore the idea of different year-cycles of the planets in our Solar System. I have created this having in mind:

- A fun way to create graphs that can have design use
- An intuitive way to understand the different dimensions of planet's orbits
- A playful tool to see the impact of logs and exponentials on a number sequence

You can check it [here!](https://github.com/arthurlunabcf/SolarSysPlot)


## How was this done?

Each planet is a vector of the length of an even number close to its year duration measured in Earth Days. So, Earth is a vector of 364 numbers, going from 0 to 1 and back to 0 again. When you plot lenghts of time larger than the planet's cycle, this sequence is repeated as necessary. You can see the sequence creation here.

```{r echo=TRUE}
    Mercury <- c(0 + (1:44)/44, 1 - (1:44)/44)
    Venus <- c(0 + (1:112)/112, 1 - (1:112)/112)
    Earth <- c(0 + (1:182)/182, 1 - (1:182)/182)
    Mars <- c(0 + (1:343)/343, 1 - (1:343)/343)
    Jupiter <- c(0 + (1:2165)/2165, 1 - (1:2165)/2165)
    Saturn <- c(0 + (1:5376)/5376, 1 - (1:5376)/5376)
    Uranus <- c(0 + (1:15317)/15317, 1 - (1:15317)/15317)
    Neptune <- c(0 + (1:30074)/30074, 1 - (1:30074)/30074)
    Pluto <- c(0 + (1:45368)/45368, 1 - (1:45368)/45368)
```

## 
You can log it, exponentient it or do a crazy transformation to it.

```{r echo = TRUE}
Reg <- Mercury; Reg[1:5]
Log <- log(Mercury); Log[1:5]
Exp <- exp(Mercury); Exp[1:5]
Crazy <- (log(Mercury))*(Mercury)^2; Crazy[1:5]
```

## Plot it!
Here I show 88 Earth Days, or 1 year on Mercury, with the Mercury Data

```{r echo = F}
library(ggplot2); 
ggplot(mapping = aes(x = 1:88)) + 
  geom_line(mapping = aes(y = Reg, color = "Regular")) + 
  geom_line(mapping = aes(y = Log, color = "Log")) + 
  geom_line(mapping = aes(y = Exp, color = "Exp")) + 
  geom_line(mapping = aes(y = Crazy, color = "Crazy")) +
  labs(x = "Earth Days", y = "values", title = "88 days on Mercury, different possibilities") +
  theme(legend.title = element_blank())



```

